---
title: "Comparison of Clusters"
output: html_document
date: "2023-03-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries  

```{r}
library(dplyr)
library(ggplot2)
library(gridExtra)

library(stringr)
library(sf)
library(tidyr)
library(tidyverse)
library(lubridate)
library(devtools)
library(janitor)
```

# to check for multicolinarity --> VIF test  

```{r}
library(car)
```
# kmeans package  
```{r}
library(stats)
library(factoextra)
```


```{r}
dd_burden.merge <- read.csv("/Users/adrianabryant/Desktop/For publication/DataFinal/dd_burden_pub.csv")

dd_burden.merge$FIPS <- str_pad(dd_burden.merge$FIPS, 5, pad = "0")

poverty <- read.csv("/Users/adrianabryant/Desktop/For publication/DataFinal/PovertyEstimates.csv")
poverty$FIPS_code <- str_pad(poverty$FIPS_code, 5, pad = "0")

NRIdata1 <- read.csv("/Users/adrianabryant/Desktop/For publication/DataFinal/NRI_Table_Counties/NRI_Table_Counties.csv")

state.shp <- st_read("/Users/adrianabryant/Desktop/For publication/DataFinal/tl_2018_us_state/tl_2018_us_state.shp")
county.shp <- st_read("/Users/adrianabryant/Desktop/For publication/DataFinal/tl_2018_us_county/tl_2018_us_county.shp")

county.shp <- filter(county.shp,!STATEFP %in% c("02","15","72","78"))
state.shp <- filter(state.shp,!STATEFP %in% c("02","15","60","66","69", "72","78"))

county.shp <- rename(county.shp, FIPS = GEOID)
state.shp <- rename(state.shp, FIPS = GEOID)



fips <- read.csv("/Users/adrianabryant/Desktop/For publication/DataFinal/FIPS.csv")
```

```{r}
NRIdata1 <- rename(NRIdata1,FIPS = STCOFIPS)
NRIdata1 <- NRIdata1[,c('FIPS',"POPULATION")]
```

```{r}
NRIdata1$FIPS <- str_pad(NRIdata1$FIPS, 5, pad = "0")
dd_burden.merge<- merge(dd_burden.merge,NRIdata1,by="FIPS",all.x=TRUE)
```

# import disaster declarations  
```{r}
PDD <- read.csv("//Users/adrianabryant/Desktop/For publication/DataFinal/PDDAllison.csv")
PDD.sub <- PDD[,c('disasterNumber..Maj..','disasterNumber..Em..',"FIPS","fyDeclared")]
PDD.sub <- mutate_all(PDD.sub,~replace_na(.,0))
PDD.sub$FIPS <- str_pad(PDD.sub$FIPS, 5, pad = "0")
PDD.sub <- filter(PDD.sub, fyDeclared == c("2010","2011","2012","2013","2014","2015","2016","2017","2018","2019"))

FREQ <- data.frame(table(PDD.sub$FIPS)) %>%
  rename(FIPS = Var1)

FREQ$FIPS <- as.character(FREQ$FIPS)
fips$FIPS <- str_pad(fips$FIPS, 5, pad = "0")

test <- merge(dd_burden.merge, FREQ, by="FIPS", all.x=TRUE)
dd_burden.merge.freq <- test %>% replace(is.na(.), 0)

```

# merging burden with poverty data
```{r}
poverty.sub <- rename(poverty,FIPS=FIPS_code)
m1 <- merge(dd_burden.merge,poverty.sub,by="FIPS",all.x=TRUE)
m1$MEDHHINC_2020 <- as.numeric(gsub(',',"",m1$MEDHHINC_2020))
```

```{r}
m1.pdd <- merge(dd_burden.merge.freq,poverty.sub,by="FIPS",all.x=TRUE)
m1.pdd$MEDHHINC_2020 <- as.numeric(gsub(',',"",m1$MEDHHINC_2020))
```

```{r}
model2 <- lm(ddratio.avg ~ burden.avg + MEDHHINC_2020,data = m1)

vif(model2)

barplot(vif(model2),main="VIF Values",horz=TRUE,col="steelblue")

model3 <- lm(ddratio.avg ~ burden.avg + PCTPOVALL_2020 ,data = m1)

vif(model3)

barplot(vif(model3),main="VIF Values",horz=TRUE,col="steelblue")

```

#testing model with disaster frequency
```{r}
model4 <- lm(ddratio.avg ~ burden.avg + MEDHHINC_2020 + Freq,data=m1.pdd)
vif(model4)

barplot(vif(model4),main="VIF Values",horz=TRUE,col="steelblue")
```

k-means information
https://towardsdatascience.com/how-to-use-and-visualize-k-means-clustering-in-r-19264374a53c

radar plot information 
https://www.datanovia.com/en/blog/beautiful-radar-chart-in-r-using-fmsb-and-ggplot-packages/

```{r}
#m2 <- m1[,c("ddratio.avg","burden.avg","POPULATION","PCTPOVALL_2020","MEDHHINC_2020")]
m2 <- m1[,c("ddratio.avg","burden.avg","POPULATION")]
#m2$MEDHHINC_2020 <- as.numeric(gsub(',',"",m2$MEDHHINC_2020))
m2 <- data.frame(scale(m2))
```

# new test data frame with ratio, avg, pop, inc,freq
```{r}
m2.v2 <- m1.pdd[,c("ddratio.avg","burden.avg","POPULATION","Freq")]
#m2.v2 <- m1.pdd[,c("ddratio.avg","burden.avg","POPULATION","MEDHHINC_2020","Freq")]
#m2.v2 <- m1.pdd[,c("ddratio.avg","burden.avg","POPULATION")]

m2.v2 <- data.frame(scale(m2.v2))
```


# kmeans with frequency value
```{r}
library(cluster)
k1.v2 <- kmeans(m2.v2,3, iter.max = 10)

p0.v2 <- fviz_cluster(k1.v2,data=m2.v2,geom="point")+ ggtitle("k = 4")
p0.v2
print(k1.v2)

elbow1.v2 <- fviz_nbclust(m2.v2, kmeans, method = "wss")
elbow1.v2
```


k mediods with revised data  
this means inclusion of : "ddratio.avg","burden.avg","POPULATION","PCTPOVALL_2020","MEDHHINC_2020"

```{r}
k2.v2 <- pam(m2.v2,4,metric="euclidean",stand=FALSE)

test$MedoidsClust <- k2.v2[["clustering"]]

county.shp$FIPS <- str_pad(county.shp$FIPS, 5, pad = "0")
test$FIPS <- str_pad(test$FIPS, 5, pad = "0")

test$MedoidsClust <- factor(test$MedoidsClust)

merge.v2 <- st_as_sf(merge(test,county.shp,by="FIPS",all.x=TRUE))
#merge.v2 <- filter(merge.v2, !(Stabr %in% c("MP","VI","PR","AS","AK","0")))


p <- ggplot()+
  geom_sf(data=merge.v2,mapping=aes(fill=MedoidsClust),color="grey50")+
  geom_sf(data=state.shp,fill=NA) +
 ggtitle("Donor Donee and Burden Medoid (pop,freq), k=4")

ggsave("/Users/adrianabryant/Desktop/For publication/DataFinal/Figure/DD_Burden_clust_pop_freq_k4_test.png", width = 6, height = 4)

```

```{r}
#table(k2[["pamobject"]][["clustering"]])
```

```{r}
library(hopkins)


h <- hopkins(m2.v2)


p <- hopkins.pval(h,3049)
```

hopkins stat 
https://github.com/prathmachowksey/Hopkins-Statistic-Clustering-Tendency

p value documentation 
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4111019/#:~:text=Being%20a%20probability%2C%20P%20can,other%20than%20due%20to%20chance

```{r}
difference <- compare_df_cols(m1,m2)
```

original data for each state 
```{r}
#df <- m1.pdd[,c("FIPS","ddratio.avg","burden.avg","POPULATION")]
#df <- rename(df,ddratio.avg.og = ddratio.avg)
#df <-rename(df,burden.avg.og = burden.avg)
#df <- rename(df,POPULATION.og = POPULATION)
#df1 <- merge(df,test,by="FIPS")

#df1.freq <- df1 %>% replace(is.na(.), 0)
#df1.freq$Cluster <- as.numeric(df1.freq$MedoidsClust)
```

# going to get some quick numbers of clusters with their original values. 

```{r}
#cluster_1 <- df1.freq %>% 
#  data.frame(filter(df1.freq$Cluster == '1'))
```

